The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-01-30 VonHolzenBergmann_MPMetaAnalysis.Rmd
Straightening out theoretical predictions

abstract: |
  As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting the speaker's variation (e.g. mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g. cat vs. hat). This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity. Our goal was to evaluate the development of mispronunciation sensitivity in infancy as well as explore the role of experimental manipulations related to theoretical questions and analysis choices. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion. The results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation modulate mispronunciation sensitivity. We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

header-includes:
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
  - \usepackage{fontspec}
  - \newfontfamily\ipa{Doulos SIL}
  - \DeclareTextFontCommand{\ipatext}{\ipa}
---

@@

@@

  At the turn of the millenium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997]. @Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition. American-English learning 18- to 23-month-olds were presented with pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct, target image in response to both types of labels, correct labels elicited more looks to the correct, target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

  In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). The study of @Swingley2000 as well as subsequent studies examining infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm probe this latter distinction. Phonological contrasts relevant for the infant language-learner are determined by their native language. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. These contrasts are therefore not innate, but must be learned. In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition. By aggregating all publicly available evidence using a meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 11 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table \@ref(tab:SummaryTable)) and of those, all possible patterns of development are found. This renders conclusions regarding developmental change in mispronunciation sensitivity difficult.

Several studies  have found evidence for *greater* mispronunciation sensitivity as children develop [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. Other studies have found *no difference* in mispronunciation sensitivity at different ages [@Swingley2000; @Bailey2002; @Zesiger2012]. For example, @Swingley2000 tested infants over a wide age range of 5 months (18 to 23 months).  They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not. At least one study has found evidence for infants to become *less* sensitive  to mispronunciations as they develop, showing a decrease in sensitivity from 18 to 24 months [@Mani2011].

  Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. With time, more phonologically similar words are learned, which may drive a need to the infant to represent familiar words with more fine phonological detail. A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980]. If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005]. One notable exception comes from @Mani2010kepstups. Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand this issue.

  An alternative explanation is the level of task difficulty infants are presented with in mispronunciation sensitivity experiments. Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands (discrimination vs. word learning) probed in a particular experiment. In a particularly demanding task, such as when the target and distractor image share the same onset phoneme, infants' ability to access the phonological detail of familiar words may be restricted. If older infants are more likely to be tested using a more demaning mispronunciation sensitivity task, this may attenuate developmental effects across studies.

  These manipulations may impact task demands, but they are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing. For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploatory analyses. We outline below first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.

  The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e. 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes. This also has consequences for task demands, as the greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.

  Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016]. In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen]. One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016]. Evidence from word-learning suggests that assymetry in sensitivity to consonant and vowel changes may develop at different times depending on the infants' native language [e.g. @Floccia2014; @Nazzi2009a]. In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence [@Floccia2014; @Nazzi2016; @Keidel2007] and whether this is impacted by the language family of the infants' native language [@Nazzi2016].

  Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations resulting in a more demanding task than medial or coda mispronunciations.

  A second question is whether the experimental context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "dog", the image of a dog would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Fernald2001a]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. 
  Most studies present infants with pictures of two name-known objects, thus ruling out the unlabeled competitor, or distractor, as possible target. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016]. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003]. This ability is developing from 18 to 30 months [@Bion2013] and we may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.

@@

In sum, the studies we have reviewed begin to paint a picture of the development of infants' use of phonological detail in familiar word recognition. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development. Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciation sensitivity. Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size. We also explore the influence of different linguistic (mispronunciation size, position, and type) and experimental (overlap between target and distractor labels; distractor familiarity) demands on the study of mispronunciation sensitivity. Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].

@@

[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` records. Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor]. To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta]. For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`. This is considered a small effect size [@Mills-Smith2015], but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated. But, as the p-curve indicated evidential value, we are confident in the overall pattern, namely that infants fixate the target even after hearing a mispronounced label.

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age and increased vocabulary size. The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages. In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size. The present results do lend some support for the proposal that mispronunciation sensitivity stays constant as infants develop. Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations. This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion.

@@

To assess whether the size of the mispornunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes. We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change). This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations. Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity [@White2008; @Mani2011], and this modertor was coded as a continuous variable.

@@

Next to the main goal of this paper, which was to evaluate the development of infants' sensitivity to mispronunciations, we also investigated the more nuanced questions often posed in studies investigating infants' mispronunciation sensitivity. We identified five additional manipulations often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age. Furthermore, considering the lack of developmental change found in our main analysis, we evaluted whether these additional manipulations were disproportionatly conducted with children of different ages, to assess whether older infants recieve more difficult tasks than younger infants.

@@

Typically, vocabulary growth is thought to invoke changes in mispronunciation sensitivity. The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995]. Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)). There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-trackers, which reduce the need for offline coding and thus make data collection much more efficient, but this has not translated to an increasing number of mispronunciation sensitivity studies also reporting vocabulary scores. We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes. More experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this is to be evaluated.

@@

This meta-analysis comprises an aggregation of almost two decades of research on mispronunciation sensitivity, finding that infants accept both correct pronunciations and mispronunciations as labels for a target image. However, they are more likely to accept correct pronunciations, which indicates sensitivity to mispronunciations in familiar words. This sensitivity was not modulated by infant age or vocabulary, suggesting that from a young age on, before the vocabulary explosion, infants’ word representations may be already phonologically well-specified. We recommend future theoretical frameworks take this evidence into account. Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of the native langauge in sensitivity to mispronunciation type (consonant vs. vowel). Furthermore, evidence of an interaction between task demands (phonological overlap between target-distractor pairs) and infant age may partially explain the lack of developmental change in mispronunciation sensitivity.

>>>>

abstract: |
  As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting speaker dependent variation (e.g. mood, voice, accent), but appropriately rejecting variation when it (potentially) changes a word's meaning (e.g. cat vs. hat). This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity. Our goal was to evaluate the development of mispronunciation sensitivity in infancy as well as explore the role of experimental manipulations related to theoretical questions and analysis choices. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion. The results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation modulate mispronunciation sensitivity. We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

header-includes:
  - \usepackage{setspace}
  - \usepackage{fontspec}
  - \newfontfamily\ipa{Doulos SIL}
  - \DeclareTextFontCommand{\ipatext}{\ipa}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
---

@@

# able to use linguistics down by copying over some front matter from the linguistics down Untitled.Rmd template
# https://yongfu.name/linguisticsdown/

#options(encoding = "UTF-8")

@@

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). Twenty years worth of studies have examined infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm to probe this latter distinction. At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997]. @Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition. American-English learning 18- to 23-month-olds were presented with pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

Why should sensitivity to mispronunciations pose a challenge to the young infant? Critically, the native language being learned determines the relevant contrasts for the infant language-learner. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. These contrasts are therefore not innate, but must be learned. As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis to assess infants' developing ability to correclty apply the phonological distinctions for their native language during word recognition. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

Regarding the change in mispronunciation sensitivity over development, only roughly half of studies have compared more than one age group on the same mispronunciation task (see Table \@ref(tab:SummaryTable)) and of those, all possible patterns of development are found. This renders conclusions regarding developmental change in mispronunciation sensitivity difficult. Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences. We thus summarize the existing empirical evidence, as well as developmental and methodological explanations for an increase, a decrease, or unchanged sensitivity to mispronunciations throughout infancy.

An *increase* in mispronunciation sensitivity is predicted by a maturation in phono-lexical representations from holistic to more detailed and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. With time, more phonologically similar words are learned, which may drive a need to the infant to represent familiar words with more fine phonological detail. A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980]. This argument is supported by the results of @Mani2010kepstups. Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Consequently, if increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship with mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005]. Furthermore, other studies testing more than one age have found *no difference* in mispronunciation sensitivity [@Swingley2000; @Bailey2002; @Zesiger2012]. Such evidence supports an early specificity hypothesis, which suggests continuity in how infants' represent familiar words. According to this account, infants represent words with phonological detail already at the onset of lexical acquisition and that this persists throughout development.

There are no theoretical accounts that would predict decreased *mispronunciation sensitivity*, but at least one study has found a *decrease* in sensitivity to small mispronunciations . @Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations (1-, 2-, and 3-feature phonological changes). Although both groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to 1-feature mispronunciations. To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below). In contrast, 18-month-olds did not show graded sensitvity, showing similar disruptions to word recognition for smaller and larger mispronunciations.

To disentangle the predictions that phonological representations are progressively specified or specified early, we investigate the relationship between mispronunciation sensitivity and both age as well as vocabulary size. But, this may not account for all variability found in the literature. Although all mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.

The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment. In a particularly demanding task, such as when the target and distractor image share the same onset (e.g. doggie and doll), infants' ability to access the phonological detail of familiar words may be restricted [@Swingley1999]. If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies. Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages .

The manipulations that might increase task demands, such as overlap between target and distractor, are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing. For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploratory analyses. We outline first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.

The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e. 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity.

Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias. A learned account predicts that a C-bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016]. In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen]. One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016]. In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to determine whether infants exhibit more sensitivity to consonant compared to vowel mispronunciations of familiar words.

Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations.

A second question is whether the context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. Note that in this case, the mispronunciation is necessarily either word-medial or –final, thus possibly creating an interaction between mispronunciation position and phonological overlap.

Most studies present infants with pictures of two known objects, thus ruling out the unlabeled competitor, or distractor, as possible target. It is thus not surprising that infants tend to look towards the target more, even when its label is mispronounced. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016]. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003]. This ability is developing from 18 to 30 months [@Bion2013] and we may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.

@@

In sum, the studies we have reviewed begin to paint a picture of the development of infants' use of phonological detail in familiar word recognition. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development. Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciation sensitivity. Because we aggregate data over various age groups, this meta-analysis can investigate the role of maturation by assessing the impact of age and vocabulary size. We also explore the influence of different linguistic (mispronunciation size, position, and type) and contextual (overlap between target and distractor labels; distractor familiarity) factors on the study of mispronunciation sensitivity. Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].

@@

[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` records, respectively. Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor]. To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta [@meta]. For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`. This is considered a small effect size [@Mills-Smith2015], but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size may be overestimated. But, as the p-curve indicated evidential value, we are confident in the overall pattern, namely that infants fixate the target even after hearing a mispronounced label.

@@

The main goal of this paper was to assess mispronunciation sensitivity and whether it is modulated by maturation with age and increased vocabulary size. In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size. Regarding age, the results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages. Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations. This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion. These findings support the arguments set by the early specification hypothesis that infants represent words with phonological detail at the beginning of the second year of life.

@@

To assess whether the size of the mispronunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes. We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change). This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations. Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity [@White2008; @Mani2011], and this moderator was coded as a continuous variable.

@@

Next to the main goal of this paper, which was to evaluate the development of infants' sensitivity to mispronunciations, we also investigated the more nuanced questions often posed in studies investigating infants' mispronunciation sensitivity. We identified five additional manipulations often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age. Furthermore, considering the lack of developmental change found in our main analysis, we evaluated whether these additional manipulations were disproportionately conducted with children of different ages, to assess whether older infants receive more difficult tasks than younger infants.

@@

In accounts predicting gradual specification of phonological representations, vocabulary growth is thought to invoke changes in mispronunciation sensitivity. The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995]. Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)). There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-trackers, which reduce the need for offline coding and thus make data collection much more efficient, but this has not translated to an increasing number of mispronunciation sensitivity studies also reporting vocabulary scores. We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes. More experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this is to be evaluated.

@@

This meta-analysis comprises an aggregation of almost two decades of research on mispronunciation sensitivity, finding that infants accept both correct pronunciations and mispronunciations as labels for a target image. However, they are more likely to accept correct pronunciations, which indicates sensitivity to mispronunciations in familiar words. This sensitivity was not modulated by infant age or vocabulary, suggesting that from a young age on, before the vocabulary explosion, infants’ word representations may be already phonologically well-specified. We recommend future theoretical frameworks take this evidence into account. Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of the native langauge in sensitivity to mispronunciation type (consonant vs. vowel). Furthermore, evidence of an interaction between task demands (phonological overlap between target-distractor pairs) and infant age may partially explain the lack of developmental change in our meta-analysis.
